\bf Service Chain Placement in SDNs \thanks{Research supported in part by Network Programming (Neptune) Consortium, Israel.}

### 2017-06-23 src/graphs.tex
foo

In this section we consider the problem on undirected (physical) graphs.
Once again we seek to embed a virtual $\sigma\tau$-path 
into a simple physical $st$-path.
Note, that we still assume that the virtual graph is a DAG.

We extend our algorithm to work also for this case as well.
Recall that the problem on general graphs cannot be approximate at all,
thus we assume in this section that the there exists an optimal embedding using
at most $k$ \emph{heavy} vertices, thus are vertices with degree greater than two.
The modified algorithm runs in time polynomial in the input length and
exponential in $k$ and achieves the same guarantees as before with high
probability.

The modified algorithm acts as follow:
let $K = {v_1, \ldots, v_k}$ be the set of heavy vertices, and let 
$\pi:[k] \to [k]$ be a random permutation.
Let $v_1, v_l \in K$ be two heavy vertices such that $\pi(v_1) < \pi(v_l)$ and
let $w_1, \ldots, w_l$ any light path between them, i.e. a path that does not
contains any other heavy vertex.
We orient the edges from $u$ to $v$, i.e. $(w_i, w_{i+1})$ for every 
$1 \leq i \leq l - 1$.
One can be verify that this can be done efficiently and that after this process
each edge become an arc and that $G$ is a DAG.

>>>>

In this section we consider the problem when the physical network is undirected.
Once again we seek to embed a virtual $\sigma\tau$-path 
into a simple physical $st$-path.
Note, that we still assume that the virtual graph is a DAG.

We extend our algorithm to work also for this case as well.
Recall that the problem on general graphs cannot be approximate at all,
thus we assume in this section that there exists an optimal embedding that uses
a physical path with at most $k$ \emph{heavy} vertices, thus are vertices with
degree greater than two (we do not assume anything about the physical network).
The modified algorithm includes a preprocessing stage that applies
random orientation to the physical network, it runs in time polynomial in the
input length and in $O(k!)$ and finds the optimal embedding with high probability.

The preprocessing stage is as follow:
let $V_h = {v_1, \ldots, v_h}$ be the set of heavy vertices, and let 
$\pi:[h] \to [h]$ be a random permutation.
Let $w_1, \ldots, w_l$ be a light path, that is, $w_1, w_l \in V_j$, 
$\forall 1 < i < l, w_i \notin V_h$, $\pi(w_1) < \pi(w_l)$, then
we direct the edges from $w_1$ to $w_l$ i.e. $(w_i, w_{i+1})$ for every $1 \leq
i \leq l - 1$.
One can verifies that this can be done efficiently and that when this process
terminates $G$ is a DAG, Figure~\ref{fig:orientation} depicts the preprocessing
stage.

\begin{figure}[h]
\input{fig-orientation}
\caption{
\label{fig:orientation}
The preprocessing stage: on the left is the undirected physical network,
Only the heavy nodes are drawn.
The numbers represent the permutation and the blue, dashed path represents a
path of an optimal embedding.
On the right side is the orientated physical network, 
note that it is enough that the internal ordering of the nodes on the blue,
dashed path is "correct" to ensure that the algorithm finds the optimal
embedding. }
\end{figure}

### 2017-06-23 src/main.tex
foo

\nonstopmode
\documentclass[draft]{article}

\input{libs}
\input{def}
\input{tikz}

\input{title}
\input{authors}

@@

\input{outline}

\bibliographystyle{plain}
\bibliography{main}

>>>>

\nonstopmode
%\documentclass[11pt]{article}
\documentclass[runningheads]{llncs}

\usepackage{amsmath,amssymb,mathtools}
%\usepackage{amsthm}
%\usepackage{fullpage}
\usepackage{xspace}
\usepackage{color,soul}
\usepackage{paralist}

% \usepackage[linesnumbered, ruled]{algorithm2e}

\usepackage[final]{microtype}
\usepackage[final]{hyperref}
\usepackage{subcaption}

% DEBUG
%\usepackage{lipsum}
\usepackage{todonotes}
%\usepackage{lineno}
%\linenumbers

% EXTRA
%\usepackage{authblk}

\input{tikz}

\def\VPN{Service Chain Placement in SDN}
\def\R{\mathbb{R}}
\def\N{\mathbb{N}}

\sloppy

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% handy commands

\newcommand{\eqdf}{\stackrel{\scriptscriptstyle \triangle}{=}}
\newcommand{\argmin}{\ensuremath{\mbox{argmin}}}
\newcommand{\argmax}{\ensuremath{\mbox{argmax}}}
\newcommand{\set}[1]{\left\{ #1 \right\}}
\newcommand{\paren}[1]{\left( #1 \right)}
\newcommand{\bit}{\set{0,1}}
\newcommand{\inv}[1]{\frac{1}{#1}}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\ceil}[1]{\left\lceil {#1} \right\rceil}
\newcommand{\floor}[1]{\left\lfloor {#1} \right\rfloor}
\newcommand{\half}{\frac{1}{2}}
\newcommand{\threehalves}{\frac{3}{2}}

\newcommand{\naturals}{\mathbb{N}}
\newcommand{\rationals}{\mathbb{Q}}
\newcommand{\reals}{\mathbb{R}}
\newcommand{\integers}{\mathbb{Z}}

\newcommand{\eps}{\varepsilon}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\scp}{\textsc{SCP}\xspace}
\newcommand{\scplong}{\textsc{Service Chain Placement}\xspace}

\newcommand{\calE}{\mathcal{E}}
\newcommand{\calG}{\mathcal{G}}
\newcommand{\calV}{\mathcal{V}}

\newcommand{\dror}[1]{\sethlcolor{yellow}\hl{Dror: #1}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{\bf Service Chain Placement in SDNs%
\thanks{Research supported in part by Network Programming (Neptune)
  Consortium, Israel.}
}

\titlerunning{Service Chain Placement in SDNs}

%\author[1]{Gilad Kutiel%
%\thanks{E-mail: \texttt{gkutiel@cs.technion.ac.il}}}

%\author[2]{Dror Rawitz%
%\thanks{Partially supported by the Israel Science Foundation
%  (grant no.~497/14).  E-mail: \texttt{dror.rawitz@biu.ac.il}}}

%\affil[1]{Department of Computer Science, Technion, Haifa, Israel}
%\affil[2]{Faculty of Engineering, Bar Ilan University, Ramt-Gan, Israel}

\author{%
Gilad Kutiel
\and
Dror Rawitz%
\thanks{Partially supported by the Israel Science Foundation
  (grant no.~497/14).  }
}

\institute{%
Department of Computer Science, Technion, Haifa 32000, Israel. \\
\email{gkutiel@cs.technion.ac.il}
\and
Faculty of Engineering, Bar Ilan University, Ramt-Gan 52900, Israel.\\
\email{dror.rawitz@biu.ac.il}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

% \begin{abstract}
% We study the allocation problem of a \emph{service chain} in a
% software-defined network that supports network function
% virtualization.
% %
% Given a network that contains servers with limited processing power
% and of links with limited bandwidth, a service chain is a sequence of
% virtual network functions (VNFs) that service a certain flow request
% in the network.
% %
% The allocation of a service chain consists of routing and VNF
% placement.  That is, each VNF from the seqeunce is placed in a server
% along a path, and it is feasible if each server can handle the VNFs
% that are assigned to it, and if each link on the path can carry the
% flow that is assigned to it.
% %
% A request for service is composed of a source and a destination in the
% network, an upper bound on the total latency, and a specification of
% all service chains that are considered valid for this request.
% %
% Each pair of server and VNF are associated with a cost for placing the
% network function in the server, and given a request, the goal is to
% find a valid service chain of minimum total cost or to identify that
% a valid service chain does not exist.
% 
% We show that even the feasibility problem is NP-hard in general
% di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
% We show that the problem is still NP-hard in DAGs and present an
% FPTAS.
% %
% Based on out PTAS, we also provide a randomized algorithm for
% instances in which the service chain passes through a bounded number
% of servers whose degree is larger than two.
% 
% ?????
% 
% Fault tolerant placement: two service chains?
% 
% FPT algorithm where the number of servers whose degree is larger than
% two is a parameter?
% \end{abstract}
% 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \section{Introduction}
% 
% 
% Computer communication networks are in constant need of expansion to
% cope with the ever growing traffic.  As networks grow, management and
% maintenance become more and more complicated.
% %
% Current developments aim to improve the utilization of network
% resources include the detachment of network applications from network
% infrastructure and the transition from network planning to network
% programming.
% 
% One aspect of network programming is to manage resources from a
% central point of view, namely to make decisions based on availability,
% network status, required quality of service, and the identity of the
% client.  Hence, a central issue is a central agent that is able to
% received reports from network components and client requests, and as a
% result can alter the allocation of resources in the networks.  This
% approach is called Software Defined Networking (SDN), where there is a
% separation between routing and management (control plane) and the
% underlying routers and switches that forward traffic (data plane) (see
% Kreutz et al.~\cite{KRVRAU15}).
% 
% A complimentary approach is Network Function Virtualization
% (NFV)~\cite{NFV12}.  Instead of relying on special purpose machines,
% network applications become virtual network functions (VNF) that are
% executed on generic machines and can be placed in various locations in
% the network.  Virtualization increases the flexibility of resource
% allocation and thus the utilization of the network resources.
% %
% Internet Service Providers (ISPs) that provide services to clients
% benefit from NFV, since it helps to better utilize their physical
% network.  In addition, when network services are virtualized, an ISP
% may support \emph{service chaining}~\cite{ServiceChaining15}, namely a
% compound service that consists of a sequence of VNFs.  Furthermore,
% one may offer a compound service a service that may be obtained using
% one of several sequences of VNFs.
% 
% In this paper we study the allocation problem of a compund request for
% a service chain in a software-defined network that supports NFV.
% Given a (physical) network that contains servers with limited
% processing power and of links with limited bandwidth, a service chain
% is a sequence of virtual network functions (VNFs) that service a
% certain flow request in the network.
% %
% The allocation of a service chain consists of routing and VNF
% placement.  That is, each VNF from the seqeunce is placed in a server
% along a path, and it is feasible if each server can handle the VNFs
% that are assigned to it, and if each link on the path can carry the
% flow that is assigned to it.
% %
% A request for service is composed of a source and a destination in the
% network, an upper bound on the total latency, and a specification of
% all service chains that are considered valid for this request.
% %
% Each pair of server and VNF are associated with a cost for placing the
% network function in the server.  This cost measures compatibility of a
% VNF to a server (infinite costs means ``incompatible'').  Given a
% request, the goal is to find a valid service chain of minimum total
% cost or to identify that a valid service chain does not exist.
% 
% 
% \dror{Explain one shot approach}
% 
% \paragraph*{\bf Related work.}
% %
% 
% Cohen et al.~\cite{CLNR15} considered VNF placement.  In their model
% the input is an undirected graph with a metric distance function on
% the edges.  clients are located in various nodes, and each client is
% interested in a subset of VNFs.  For each node $v$ and VNF $\alpha$,
% there is a setup cost associated with placing a copy of $\alpha$ at
% $v$ (multiple copies are allowed), and there is a load that is induced
% on $v$ for placing a copy of $\alpha$.  Furthermore, each node has a
% limited capacity.  Also, each copy of a VNF can handle a limited
% amount of clients A solution is the assignment of each client to a
% subset of nodes, each corresponding to one of its required VNFs.  The
% cost of a solution is the total setup costs plus the sum of distances
% between the clients and the node from which they get service.
% %
% Cohen et al.~\cite{CLNR15} gave bi-criteria approximation algorithms
% for various versions of the problem, namely algorithms that compute
% constant factor approximations that violate the load constraints by a
% constant factor.
% %
% It is important to note that in this problem does not consider
% routing, and also it assumes unordered VNF subsets.
% 
% Even, Medina, and Patt-Shamir~\cite{EMP16} studied online path
% computation and VNF placement.  They considered service chain requests
% that arrive in an online manner.  Each request is a a flow with a
% high-level specification of routing and VNF requirements.  Each VNF
% can be performed by a specified subset of servers in the system.  Upon
% arrival of a request, the algorithm either rejects the request or
% accepts it and with a specific routing and VNF assignment, under given
% server capacity constraints.  Each request has a benefit that is
% gained if it is accepted, and the goal is to maximize the total
% benefit.
% %
% Even, Medina, and Patt-Shamir~\cite{EMP16} proposed an algorithm that
% copes with requests with unknown duration without preemption by using
% a third response, which is refer to as “stand by”, whose competitive
% ratio is $O(\log (knb_{\max})$, where $n$ is the number of nodes,
% $b_{\max}$ is an upper bound on a request benefit per time unit, and
% $k$ is the maximum number of VNFs of any service chain.  This
% performance guarantee holds for the case where the processing of any
% processing request in any possible service chain is never more than
% $O(1/(k \log (nk)))$ fraction of the capacity of any network
% component.
% 
% Even, Rost, and Schmid~\cite{ERS16}
% 
% \dror{finish}
% 
% \paragraph*{\bf Our results.}
% %
% We show that even the feasibility problem is NP-hard in general
% di-graphs.  Hence we first focus on directed acyclic graphs (DAGs).
% We show that the problem is still NP-hard in DAGs and present an
% FPTAS.
% %
% Based on out PTAS, we also provide a randomized algorithm for
% instances in which the service chain passes through a bounded number
% of servers whose degree is larger than two.
% 
% ?????
% 
% \bigskip
% 
% 
% 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \section{Preliminaries}
% 
% 
% \paragraph*{\bf Model.}
% %
% The \scplong (\scp) input is composed of three components, a physical
% network, a virtual specification, and placement costs:
% \begin{description}
% \item[Physical network:]
% %
%   The physical network is a digraph $G = (V,E)$.  Each node $v \in V$
%   has a non-negative processing capacity $p(v)$, and each directed
%   edge $e \in A$ has a non-negative bandwidth cap $b(e)$.
% 
% \item[Virtual specification:]
% %
%   The description of a request for a service chain consists of a
%   physical source $s \in V$, a physical destination $t \in V$, and a
%   directed acyclic graph (DAG) $\calG = (\calV,\calE)$.
% %
%   Without loss of generality, we assume that $p(s) = p(t) = 0$.  
% %
%   The DAG $\calG$ has a source node $\sigma \in \calV$ and a
%   destination $\tau \in \calV$ Each node $\alpha \in \calV$ represent
%   a VNF that has a processing demand $p(\alpha)$.  Without loss of
%   generality, we assume that $p(\sigma) = p(\tau) = 0$.  Each edge
%   $\eps \in \calE$ has a bandwidth demand $b(\eps)$.
%   
% \item[Placement costs:]
% %
%   There is a non-negative cost $c(\alpha,v)$ for placing the VNF
%   $\alpha$ in $v$.  We assume that $c(\sigma,s) = 0$ and $c(\sigma,v)
%   = \infty$, for every $v \neq s$.  Similarly, we assume that
%   $c(\tau,t) = 0$ and $c(\tau,v) = \infty$, for every $v \neq t$.
% \end{description}
% 
% A solution consists of the following:
% \begin{description}
% \item[Virtual path:] A path from $\sigma$ to $\tau$ in $\calG$, namely
%   a sequence of vertices $\alpha_0,\ldots,\alpha_\ell$, where
%   $\alpha_0 = \sigma$, $\alpha_\ell = \tau$, and
%   $(\alpha_j,\alpha_{j+1}) \in \calE$, for every $j \in
%   \set{0,\ldots,\ell-1}$.
% 
% \item[Physical path:] A simple path from $s$ to $t$ in $G$, namely a
%   sequence of node $v_0,\ldots,v_k$, where $v_0 = s$, $v_k = t$, and
%   $(v_i,v_{i+1}) \in E$, for every $i \in \set{0,\ldots,k-1}$.
%   
% \item[Placement:] A function $f$ that maps the virtual path to the
%   physical path.  Formally, a placement is a function $f:
%   \set{\alpha_0,\ldots,\alpha_\ell} \to \set{v_0,\ldots,v_k}$
%   such that
% \begin{enumerate}
% \item If $f(\alpha_j) = v_i$ and $f(\alpha_{j+1}) = v_{i'}$, then $i
%   \leq i'$.
% \item $b(\alpha_j,\alpha_{j+1}) \leq b(v_i,v_{i+1})$, for every
%   $(v_i,v_{i+1}) \in \bar{f}(\alpha_j,\alpha_{j+1})$, where
%   $\bar{f}(\alpha_j,\alpha_{j+1})$ to be the set of physical edges
%   that correspond to it, i.e.,
% \[
% \bar{f}(\alpha_j,\alpha_{j+1}) \eqdf \set{(v_i,v_{i+1}) : i' \leq i < i''}
% ~,
% \]
%   where $f(\alpha_j) = v_{i'}$ and $f(\alpha_{j+1}) = v_{i''}$.
% 
% \item $\sum_{\alpha \in f^{-1}(v)} p(\alpha) \leq p(v)$, where
%   $f^{-1}(v) \eqdf \set{\alpha : f(\alpha) = v}$.
%  
% \end{enumerate}
% \end{description}
% 
% An example of an \scp instance and a solution is given in
% Figure~\ref{fig:solution}.
% 
% \begin{figure}
% \centering
% \scalebox{1}{
% \input{fig-embedding}
% }
% \caption{???}
% \label{fig:solution}
% \end{figure}
% 
% The cost of a placement $f$ is:
% \[
% \sum_j c(\alpha_j,f(\alpha_j))
% ~.
% \]
% In \scp the goal is to find a feasible placement of a virtual path
% into the physical DAG that minimizes the cost.
% 
% %%%%%
% 
% We also consider an extended version of \scp in which each physical
% link causes a delay and there is an upper bound $T$ on the total
% delay.  More formally, each pair of a virtual edge $\eps$ and physical
% edge $e$ is associated with a latency $t(\eps,e)$.
% %
% Given a placement $f: \set{\alpha_0,\ldots,\alpha_\ell} \to
% \set{v_0,\ldots,v_k}$, the total latency of the solution is given by
% \[
% T(f) = \sum_j \sum_{e \in \bar{f}(\eps)} t(\eps,e)
% ~.
% \]
% In this case there is an additional constraint that $T(f) \leq T$.
% 
% 
% %%%%%
% 
% \paragraph*{\bf Definitions and notation.}
% %
% Define $n_p \eqdf \abs{V}$ and $m_p \eqdf \abs{E}$.  Similarly, define
% $n_v \eqdf \abs{\calV}$ and $m_v \eqdf \abs{\calE}$.
% 
% Given a virtual DAG $\calG$, we assume the existence of a topological
% sorting of the vertices and write $\alpha \prec_v \beta$ if $\alpha$
% precedes $\beta$ in this ordering.  If the physical network is a DAG,
% then we make a similar assumption and write $v \prec_p u$ if $v$
% precedes $u$ in this ordering.
% 
% 
% 
% 
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% \section{Hardness}
% 
% In this section we present two hardness results.  First, we show that
% even the feasibility question of \scp is NP-hard, and therefore no
% approximation algorithm exists for \scp.  In addition, we show that
% \scp is NP-hard even if $\abs{V \setminus \set{s,t}} = 1$.  We also
% show that \scp is NP-hard even if both the physical network and the
% virtual DAG are simple paths.
% 
% We show that finding a feasible solution is NP-hard.
% 
% \begin{theorem}
% Feasibility of \scp is NP-hard
% \end{theorem}
% \begin{proof}
% We use a reduction from \textsc{Hamiltonian Path} that is known to be
% NP-hard~\cite{GarJoh79}.
% %
% Given an instance $H$ of \textsc{Hamiltonian Path} we construct an
% instance of \scp.  For the physical network we have that $G$, where
% $V(G) = V(H) \cup \set{s,t}$, and $E(G) = E(H) \cup \set{(s,v),(v,t) :
%   v \in V(H)}$.  In addition, $p(v) = 1$, for every $v$, and $b(e) =
% 1$, for every $e$.  The virtual DAG $\calG$ is a path containing $n+2$
% virtual functions, $\sigma = \alpha_0, \alpha_1, \ldots, \alpha_n,
% \alpha_{n+1} = \tau$, where $p(\alpha_i) = 1$, for every $i \in
% \set{1,\ldots,n}$.  Also, $b(\alpha_i,\alpha_{i+1}) = 1$, for every
% $i$.
% 
% The construction can clearly be computed in polynomial time.
% %
% An Hamiltonian Path in $G$, induces a \scp solution that follows the
% path, i.e., $\alpha_i$ is placed in the $i$th vertex along the path.
% %
% One the other hand, since all demands and capacities are $1$, no two
% VNFs can share a physical node.  Hence a \scp solution induces an
% Hamiltonian path.
% %
% \qed
% \end{proof}
% 
% Next, we show that \scp is NP-hard even if the physical network is a
% DAG.
% 
% \begin{theorem}
% \scp is NP-hard, even if $\abs{V \setminus \set{s,t}} = 1$.
% \end{theorem}
% \begin{proof}
% The prove the theorem using a reduction from \textsc{Partition}.
% Given a \textsc{Partition} instance $\set{a_1, \ldots, a_n}$ we
% construct an \scp instance as follows.
% %
% The physical network $G$ contains three nodes: $s$, $v$, and $t$, and
% there are two edges $(s,v)$ and $(v,t)$.  The capacity of $v$ is $p(v)
% = \half \sum_i a_i$.  Edge capacities are zero.
% %
% The virtual DAG is composed of $2n+2$ vertices, namely
% \[
% \calV
% = \set{\sigma,\tau}
%   \cup \set{\alpha_1, \ldots, \alpha_n}
%   \cup \set{\beta_1, \ldots, \beta_n}
% ~.
% \]
% Also,
% \[
% \calE
% = \bigcup_i \set{ \set{\alpha_i,\beta_i} \times \set{\alpha_{i+1},\beta_{i+1}} } 
%   \cup
%   \set{ (\sigma,\alpha_1), (\sigma,\beta_1), (\alpha_n,t), (\beta_n,t) }
% ~.
% \]
% The DAG is shown in Figure~\ref{fig:dag}.
% %
% The demands are $p(\alpha_i) = a_i$ and $p(\beta_i) = 0$, for every
% $i$.  Also, $b(\eps) = 0$, for every $\eps \in \calE$.  The costs are:
% $c(\alpha_i,v) = 0$ and $c(\beta_i,v) = a_i$, for every $i$.
% 
% The \scp instance can be computed in polynomial time.
% %
% Also, it is not hard to verify that $a \in \textsc{Partition}$ if and
% only if there exists a solution whose cost is $\half \sum_i a_i$.
% %
% \qed
% \end{proof}
% 
% \begin{figure}
% \centering
% \input{fig-reduction}
% \caption{???}
% \label{fig:dag}
% \end{figure}
% 
% \dror{Figure 2: source and destination should be fixed}
% 
% \begin{theorem}
% \scp is NP-hard, even if both the physical network and the virtual DAG
% are paths.
% \end{theorem}
% \begin{proof}
% 
% \dror{reduction from partition using latency}
%   
% %
% \qed
% \end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Algorithm}
\input{algorithm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Latency}
\input{latency}

\section{Undirected Graphs}
\input{graphs}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{abbrv}
\bibliography{chain}
